European or American? A re-examination of the transatlantic influence over the IMF

### 2025-07-15 manuscript/manuscript.qmd
Add robustness draft

>>>>

## Robustness: Continental Preference

One plausible alternative explanation for the strong association between European influence and favourable IMF lending outcomes is that European powers might be disproportionately favouring fellow European recipients. To evaluate this possibility, we examine whether the effect of European influence differs significantly between European and non-European countries.

We interact the European influence variable (`EUP Influence`) with a binary indicator for whether the recipient is a European country (`European recipient`), and re-estimate the main models accordingly. The results are presented in @tbl-results-europe.

Contrary to the hypothesis of regional favouritism, the interaction terms are either statistically insignificant or, when significant, indicate a *weaker* effect of European influence for European borrowers. For example, in the loan-to-GDP ratio and participation rate models, the negative and significant interaction terms suggest that European influence is associated with *less favourable* outcomes for European recipients compared to non-Europeans.

These findings suggest that the observed European influence is not driven by a preference for geographically proximate countries, but instead reflects a broader institutional influence over the IMF. In other words, European powers appear to exercise their influence globally, rather than selectively favoring their regional neighbours.
